---
title: "p8105_hw5_zz3039"
output: github_document
date: "2022-11-13"
---

```{r chunk_library, include=FALSE}
library(tidyverse)
library(purrr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%")

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis")
```


## Problem 2

Imported data:
```{r}
homicide_data = 
  read.csv("./data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = paste(city, state, sep=", ")
  ) %>% 
  select(city_state, - city, - state, everything())
```

Summed over number of cases:
```{r}
homi_sum = 
  homicide_data %>% 
  group_by(city_state) %>% 
  summarize(
    n_homicide = n(),
    n_unsolved = sum(disposition != "Closed by arrest"))
```

Prop.test for baltimore:
```{r}
balti = 
  homi_sum %>% 
  filter(city_state == "Baltimore, MD")

balti_test = 
  prop.test(balti$n_unsolved, balti$n_homicide) %>% 
  broom::tidy() %>% 
  mutate(
    conf.low = round(conf.low, digits = 3),
    conf.high = round(conf.high, digits = 3)
  )

tibble(
  balti_es = balti_test$estimate,
  balti_ci = paste(balti_test$conf.low, balti_test$conf.high, sep=", ")
)
```

Prop.test for each city:
```{r}
homi_prop = 
  homi_sum %>% 
  mutate(
    prop = 
      map2(.x = n_unsolved, .y = n_homicide, ~prop.test(x = .x, n = .y)),
    prop_test =
      map(prop, broom::tidy)) %>% 
  select(city_state, prop_test)
  

homi_prop_extrct = 
  homi_prop %>% 
  unnest(prop_test) %>%
  select(city_state, estimate, conf.low, conf.high) %>% 
  mutate(
    estimate = round(estimate, digits = 3),
    conf.low = round(conf.low, digits = 3),
    conf.high = round(conf.high, digits = 3),
    CI = str_c("(", conf.low,", ", conf.high, ")")) %>% 
  select(city_state, estimate, CI, everything())
```

Plot:
```{r}
homi_prop_extrct %>% 
  mutate(
    city_state = fct_reorder(city_state, estimate)
  ) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point(color = "grey") +
  geom_errorbar(mapping=aes(x = city_state, ymin = conf.low, ymax = conf.high), width=0.05, size=1, color="light blue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Problem 3

Wrote function and simmed:
```{r}
p3_sim = function(n, mu, sigma = 5) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )

  t_test =
    t.test(sim_data$x, alternative = "two.sided") %>% 
    broom::tidy()
  
  tibble(
    mu_hat = mean(sim_data$x),
    p_value = t_test$p.value
  )
}

output = vector("list", 5000)

for (i in 1:5000) {
  output[[i]] = p3_sim(n = 30, mu = 0)
}

sim_results = bind_rows(output)
sim_results
```
  t_test = 
    t.test(sim_data$x, alternative = c("two.sided"), mu = mu) %>% 
    broom::tidy()
  


Repeated for different mus:
```{r}
sim_results_mus = 
  expand_grid(
    sample_size = 30,
    mu = c(1, 2, 3, 4, 5, 6),
    iter = 1:5000
  ) %>% 
  mutate(
    estimate_df = map2(.x = sample_size, .y = mu, ~p3_sim(n=.x, mu=.y))
    ) %>% 
  unnest(estimate_df)

sim_results_mus
```

Plot-power/mean
```{r}
sim_results_mus %>% 
  group_by(mu) %>% 
  summarize(
    power = sum(p_value < 0.05)/5000
  ) %>% 
  ggplot(aes(x = mu, y = power)) +
  geom_line() +
  labs(
    x = "True mean",
    y = "Power"
  )
```
The power of the test increases as the simulation size increases.


Plot-estimated/true
```{r}
sim_results_mus %>% 
  group_by(mu) %>% 
  summarize(
    mu_est = mean(mu_hat)
  ) %>% 
  ggplot(aes(x = mu, y = mu_est)) +
  geom_point() +
  geom_line() +
  labs(
    title = "All Simulations",
    x = "True mean",
    y = "Estimated mean"
  )

sim_results_mus %>% 
  filter(p_value < 0.05) %>% 
  group_by(mu) %>% 
  summarize(
    mu_est = mean(mu_hat)
  )%>% 
  ggplot(aes(x = mu, y = mu_est)) +
  geom_point() +
  geom_line() +
  labs(
    title = "Simulations with Null Rejected",
    x = "True mean",
    y = "Estimated mean"
  )
```
Is the sample average of mu across tests for which the null is rejected approximately equal to the true value of mu? Why or why not?

